# Developing Data Products Week 2 Assignment
### By Ivo Alabe
### October 6, 2020

# 1. Instructions

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on GitHub Pages.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

# 2. Review Criteria

The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Does the web page feature an interactive map that appears to have been created with Leaflet?

# 3. Web Page with Leaflet

I`m from Bolivia. Here you have a map from Bolivia, South America.

````{r}
library(leaflet)
library(dplyr)

my_map <- leaflet() %>%
addTiles() %>%
        setView(lng=-63.5886, lat=-16.2901, zoom = 4)
my_map

````
Here you have a map from the "Cristo de la Concordia", the most famous place to visit in Cochabamba.  You can find information about it in the link.

````{r}
ccc <- c("<a href= 'https://es.wikipedia.org/wiki/Cristo_de_la_Concordia'>Cristo de la Concordia</a>")
leaflet() %>%
addTiles() %>%
addMarkers(lat=-17.3846, lng=-66.1345, popup = ccc)
 
           
````

Thank you!